Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-19 paper.tex
Update on Overleaf.

\begin{abstract}
An intuitive and easily accessible information on a quantity measured over time is whether it increases or decreases.
Trending refers to the ability to predict the direction of change for a true variable accurately. 
Thus, an appropriate assessment of the trending ability is crucial for measurements, nowcasts, and forecasts for decision-makers. 
While the current practice of evaluating signals is based on averaging over local deviation measures, we review and introduce trending measures that consider whether the direction of development fits the quantity of interest. 
We formalize the concept of trending for all application areas and present quantitative measures. 
Using bootstrap confidence intervals and exclusion areas, we provide extensions for noisy data and estimation uncertainty.
We review and present new visualization techniques to assess the local trending behaviors and enlarge the scope to probabilistic nowcasts and forecasts. 
We apply the methods to three large data applications: COVID-19-nowcasting, emergency department arrival forecasting, and invasive and non-invasive blood pressure measurements.
\end{abstract}

\listoftodos

>>>>

\begin{abstract}
An intuitive and easily interpretable information on a quantity measured over time is whether it increases or decreases.
Trending refers to the ability to predict or measure the direction of change for a true variable accurately. 
An appropriate assessment of the trending ability is crucial for measurements, nowcasts, and forecasts for decision-makers, as it enables them to assess the method's credibility accurately.
While the current practice of evaluating signals is based on averaging over local deviation measures, we review and introduce trending measures that consider whether the direction of development fits the quantity of interest. 
We formalize the concept of trending for all application areas and present quantitative measures. 
Using bootstrap confidence intervals and exclusion areas, we provide extensions for noisy data and estimation uncertainty.
We review and present new visualization techniques to assess the local trending behavior and enlarge the scope to probabilistic nowcasts and forecasts. 
We apply the methods to three large data applications: COVID-19-nowcasting, emergency department arrival forecasting, and invasive and non-invasive blood pressure measurements.
\end{abstract}

% \listoftodos

### 2024-03-19 sections/01-introduction.tex
Update on Overleaf.

The evaluation of measurement, prediction, and forecasting methods becomes increasingly important and sophisticated as technologies and data availability enable their application in more and more fields. 
Conventionally, methods are evaluated using distance measures of local differences between predictions (or measurements) and target values into account. 
These measures fail to consider whether the right direction of change is predicted or measured correctly.
The information about whether an increase or decrease is predicted correctly is crucial when making decisions based on the estimator's prediction results. 
In the following, we provide an overview of the characteristics and current evaluation schemes of the three application areas: measurement, forecasting, and nowcasting.
We highlight why trending evaluation is highly relevant in the respective fields.

>>>>

The evaluation of measurement, prediction, and forecasting methods becomes increasingly important and sophisticated as technologies and data availability enable their application in more and more fields. 
Conventionally, methods are evaluated using distance measures of local differences between predictions (or measurements) and target values. 
These measures do not consider whether the right direction of change is predicted or measured.
The information about whether an increase or decrease is predicted correctly is crucial when making decisions based on the estimator's prediction results. 
In the following, we provide an overview of the characteristics and current evaluation schemes of the three application areas: measurement, forecasting, and nowcasting.
We highlight why trending evaluation is highly relevant in the respective fields.
